An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-17 Revision/response.tex

%%%%%%%%%%%%%%%%%%%%%% D2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{In Section 1.1, I could not find convincing references for the requirements in practical applications.
			[12] and [36] are research papers only, but not from real applications.}
	\end{detailed}
}

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% D3 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{In Definition 2.3, $ s_1 $ and $ s_n $ should be replaced with $ a_1 $ and $ a_n $ , respectively.}
	\end{detailed}
}

\noindent
\textbf{Response:} 
We sincerely apologize for the misuse of notation in Definition 2.3. This has been corrected in the revised version. Thank you for pointing it out.

@@

%%%%%%%%%%%%%%%%%%%%%% D4 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{ In Section 4.1, please clarify the URL of the implementation of each method.}
	\end{detailed}
}

\noindent
\textbf{Response:} 
Thank you for the suggestion! Since there are multiple methods, listing all URLs in Section 4.1 would be overwhelming. Instead, we have added the corresponding URLs in footnotes on the relevant pages throughout the paper.

@@

\noindent
\textbf{Response:}

%%%%%%%%%%%%%%%%%%%%%% D2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{Section 4.2.1: It is important to run the experiments on larger datasets, e.g. 100 M vectors, or 1B bigann. Otherwise, differences will not show.
			Also, build time parameters such as Radius and Length which impact the Recall need to be considered.
			Also, approaches for partitioning and merging for building very large indexes need to be considered.
			Please also document whether quantization is included in index build time.
			There is no explanation why Vamana is not included in Figure 7.}
	\end{detailed}
}

\noindent
\textbf{Response:} 
Thanks to the reviewer for suggesting that there is no explanation in Figure 7 why Vamana is not included. Figure 7 is an experiment on multi-label construction and search, and the Boolean logic of multi-label search is AND. The two algorithms using Vamana, FilteredVamana and StitchedVamana, only support Boolean logic OR for multi-label search, so we did not include them. We will add an explanation of this in the paper.

All the evaluated algorithms in our experiments build the index in a one-shot manner, without applying any partitioning or merging strategies.
Additionally, although some of the methods we used—such as FAISS, PUCK, DiskANN, and Milvus—support vector quantization during index construction, we did not enable quantization in any of our experiments. Therefore, the reported index build times do not include quantization.

### 2025-07-17 Revision/response.tex

\noindent
\textbf{Response:}

\setcounter{detailed}{0}

%%%%%%%%%%%%%%%%%%%%%% D1 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{Section 2.2. Graph based and IVF are well known. Missing in the index description is the implementation of attributes for AF and RF as the section is call hybrid ANN.}
	\end{detailed}
}

\noindent
\textbf{Response:}
Thank you for your suggestion! We recognize that the original manuscript did not clearly explain how attribute filtering (AF) and range filtering (RF) are embedded into standard Graph-based and IVF-based index structures.

To address this, we have revised Section 2.2 to summarize how the algorithms discussed in this paper implement hybrid query functionality based on these foundational indexing structures (with detailed implementation provided in Section 3):

For Graph-based indexes, we describe the typical approaches of embedding attribute and range constraints by associating metadata with graph vertices or edges. Specifically, attribute filtering (AF) is usually achieved by annotating vertices or edges with attribute information, enabling the traversal algorithm to skip nodes or edges that do not satisfy the query predicates (e.g., NHQ, Filtered-DiskANN, ACORN). In contrast, range filtering (RF) typically involves annotating edges with valid attribute intervals so that traversal proceeds only along edges that satisfy the query's range constraints, effectively reducing the search space (e.g., SeRF, DSG).

For IVF-based indexes, we point out that their inherent pre-filtering mechanism naturally supports hybrid query functionality. In particular, attribute and range filtering can be implemented by directly excluding irrelevant vectors during intra-cluster distance computations. Furthermore, we highlight the hierarchical partitioning approach based on attributes, which further divides clusters into finer-grained sub-partitions, significantly improving filtering efficiency (e.g., CAPS, PUCK).

### 2025-07-17 VLDB2026/main.tex
update 2.2 revison
Update main.tex

	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts. Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts. In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.

>>>>

	As illustrated in Figure~\ref{fig:exp_3_1}, the evaluated algorithms exhibit varying degrees of sensitivity to attribute distribution shifts. \textcolor{blue}{The closer the four curves (corresponding to the four distributions) in the figure approach each other, the less the algorithm is affected by attribute distributions. Conversely, the farther they diverge, the more significant the impact of attribute distributions on the algorithm becomes.} Specifically, ACORN, Milvus, Puck, CAPS, StitchedVamana, and UNG demonstrate strong robustness to such shifts. In contrast, Faiss, FilteredVamana, NHQ, VBASE, and PASE show notable sensitivity.
